---
title: "Report on Conference Registration for Arise Nigeria, 22-23 January 2019"
author: "DevSolutions Ltd"
date: "17 February 2019"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
lapply(c("RSQLite",
         "here",
         "knitr",
         "magrittr",
         "tidyverse"),
       library,
       character.only = TRUE)
opts_chunk$set(echo = FALSE)
```

# Introduction
Nehemiah Apostolic Resource Centre (NARC) hosted a 2-Day conference tagged *Arise Nigeria* from 22-23 January 2019 at M & M Events Centre, Area 11 Garki, Abuja. DevSolutions was called upon to handle on-site conference registrations.

# Activity
## Pre-conference
NARC had already started pre-conference registration via an online service [Eventbrite](https://www.eventbrite.com) before our company was brought on board.

A training session organised for registrants held in the premised of NARC in the evening of Monday 21 January, 2019. During the session, a customized electronic data entry format was introduced with practical demonstration on its usage. Out of 9 persons pencilled down as registrants, 6 attended the training session. Other relevant staff of the Centre were present.

Also visits were made to the conference venue to ensure that adequate arrangements were put in place for the team's assignment.


# Exploratory Data Analysis
```{r dependencies, message=FALSE}
source(file.path(here(), 'data', 'helpers.R'))
```

```{r load data}
cnx <- dbConnect(SQLite(), dataDirPath('arise_nigeria.db'))
df <- dbReadTable(cnx, 'all_registrations')
dbDisconnect(cnx)
```

## Gender of Participants
```{r plot gender}
ggplot(data = subset(df, !is.na(gender)), aes(gender)) +
  geom_bar(fill = "darkgreen") +
  ggtitle('Gender of participants')
```

```{r}
genderChiStat <- chisq.test(table(df$gender))
```
The gender difference of participants is `r ifelse(genderChiStat$p.value < .001, "", "not")` statistically significant.

## Location of Participants
Interestingly, the majority of participants who came from outside Abuja were from neighbouring Suleja (`r round(sum(df$location == "SULEJA", na.rm = TRUE) / length(df$location) * 100, digits = 2)`% of participants).
```{r plot location}
df %>%
  subset(!is.na(location) & location != 'ABUJA') %>% 
  group_by(location) %>% 
  summarise(n = n()) %>% 
  mutate(index = seq_len(nrow(.))) %>% 
  ggplot(aes(index, n)) +
  geom_label(aes(label = location, fill = location)) +
  ggtitle('Participants coming from outside Abuja') +
  ylab("Count") +
  theme(legend.position = 'none')
```


```{r}
df$location %>% 
  table(dnn = "Location") %>% 
  sort(decreasing = TRUE) %>% 
  head(10L) %>% 
  kable(caption = "Top Ten Location of Participants")
```

## Occupation of Participants
Expectedly the majority of participants were of the clergy. However, the distribution of participants indicate that a large proportion of them were students, followed by entrepreneurs, civil/public servants and artisans - in that order. 
```{r plot occupation}
dfNoNaOccup <- subset(df, !is.na(occupation))
ggplot(data = dfNoNaOccup, aes(fct_infreq(occupation))) +
  geom_bar(fill = "blue") +
  coord_flip() +
  ggtitle("Occupation of Participants") +
  xlab("Occupation type") +
  theme(axis.text.y = element_text(size = 5),
        axis.title.y = element_text(face = "bold"))
```

**In fact, the distribution of participants' occupation is very interesting, as there were proportionally almost as many students as there were clergymen/women (`r round(sum(dfNoNaOccup$occupation == 'STUDENT') / length(dfNoNaOccup$occupation), 2) * 100`% students to `r round(sum(dfNoNaOccup$occupation == "CLERGY") / length(dfNoNaOccup$occupation) %>% round(2), 2) * 100`% clergy).**

# Challenges
1. Late arrival of laptops and non-availability of internet made it difficult for the already prepared data management package to be installed on the computers. At the end of the day, the team had to resort to entering the data onto spreadsheets.

2. Inadequate staff: As stated, fewer registrants worked on the first day of the event. The were differences among the registrants in terms of their effectiveness and this was found to be statistically significant.

3. Discrepancy between the data collected on site and pre-event registrations.

```{r}
df %>% 
  count(registrant) %>% 
  ggplot(aes(x = reorder(registrant, n), y = n, fill = ifelse(registrant == "Eventbrite", "Highlighted", "Normal"))) +
  geom_bar(stat = "identity") + 
  coord_flip() +
  ggtitle("Work done by Registrants") +
  xlab("Name of Registrant") +
  theme(axis.title.y = element_text(face = "bold"),
        legend.position = "none")
```

```{r registrants chisq, include=FALSE}
chisq.test(table(df$registrant))$p.value
```

Statistically, the p-value of the distribution (i.e. the $\chi^2$ goodness-of-fit test) indicate that the discrepancy in the work done by registrants is unlikely to have happened by chance. This result did not change even after the exclusion of the pre-event registrations from the analysis i.e. those done via "Eventbrite" (highlighted in the chart).

# Recommendations
From the foregoing, we would like to make the following suggestions to the organizers for improved results on conference registrations for subsequent editions of *Arise Nigeria*:

1. Timely provision of field equipment, especially laptops, to enable the proper setup of the registration toolkit.
2. Proper staffing by improving selection and training.
3. Target students in the follow-up action of this edition as well as in future conferences.
4. Collection of registration data before and during the event should follow the same format. 
