---
output:
  md_document:
    variant: markdown_github
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  eval = FALSE,
  comment = "#>",
  fig.path = "README-"
)
```

# ariseng
This package is for collecing data on Particpant Registration for the Arise Nigeria Conference, Abuja, Nigeria.

## How To Use
### Install R
Install the executable normally. Start R on the command line of Window Powershell with this code

```
rterm
```

If you get an error, add R to the path by going to *WinKey &gt; Advanced System Settings* and then click on *Environment Variable*. Under *System variables*, look for and edit the `Path` by adding this line to already existing variables. For instance, for a 64-bit machine

```
C:\Program Files\R\R-3.5.2\bin\x64
```

If using a machine lower than Windows 10, add it to the `PATH` string and remember to add a semicolon (`;`) at the end.

### Install package
After installing R, the `ariseng` package can be installed with the following code:

```{r}
if (!requireNamespace('remotes'))
  install.packages('remotes')
remotes::install_github("DevSolutionsLtd/AriseNg/ariseng")
```

### Install project dependencies
The `ariseng` package facilitates installation of dependencies needed for the data entry form to work. To perform this step, use the following line of code and follow any prompts:

```{r}
fetch_dependencies()
```

### Collect data settings
The variables of interest have been pre-set in a project file named `arise.dte`. Running the function

```{r}
fetch_settings()
```

will make that file available in the working directory, `getwd()`. If the user wants to save the settings to a different directory, a string containing the path to the chosen directory is passed as an argument to `path` i.e.

```{r}
fetch_settings(path = 'C:/path/to/save/settings/to/')
```

### Open the data entry form
```{r}
library(DataEntry)
DataEntry()
```

---
Report any issue to the maintainer at <victor@dev-solu.com>